Wireless smart monitoring energy system: a proof of concept

### 2021-03-26 paper/main.tex
system res

	\section{System results}
	We used Wireshark to monitor our network while running the system. Generally, TCP traffic worsens the performances of UDP in wireless applications. In particular, during the test, we had both TCP and UDP third-party traffic, in particular, we had an Apex Legends game (UDP) and normal web navigation (TCP). The main objective of the test was to check the efficacy of our version of reliable UDP, so the focus was on the reception of acknowledgments by the server. The packets are sent to the correct client, even in a scenario with different traffic types. The traffic generated by the system is not much as can be seen in Figure~\ref{fig:grafico}.

>>>>

	\section{System results}
	Generally, TCP traffic worsens the performances of UDP in wireless applications. To check that this is not the case with our system,
	we used Wireshark to monitor our network while it was running. In particular, during the test, we had both TCP and UDP third-party traffic, in particular, we had an Apex Legends game (UDP) and normal web navigation (TCP). The main objective of the test was to check the efficacy of our version of reliable UDP, so the focus was on the reception of acknowledgments by the server. The packets are sent to the correct client, even in a scenario with different traffic types. The traffic generated by the system is not much as can be seen in Figure~\ref{fig:grafico}. While the test was successful it only had two plugs, one of them simulated. To achieve more realistic results the simulated plug generates more traffic than a real plug.
